RJObject Paper

### 2014-06-23 Documents/Paper/ms.tex
Labels and more talking

\subsection{Proposals that modify $N$}
The first kind of proposal we consider are proposals that change the
dimension of the model, i.e. proposals that change the value of $N$. By
necessity, these will also change the parameters $\{x_i\}_{i=1}^N$ because
the number of parameters will be changed. The proposals used here are
traditionally called {\it birth and death} proposals.

@@

\subsection{Proposals that modify objects}
We now consider a proposal distribution that modifies one or more of the
objects $\{x_i\}$, while keeping the number of objects $N$, as well as the
hyperparameters $\alpha$, fixed.

@@

\subsection{Proposals that change the hyperparameters, keeping the objects fixed}
Another kind of proposal that we will consider is a proposal that keeps all of
the objects fixed in place (i.e. leaves $\{x_i\}$) unchanged, but changes
the hyperparameter(s) from their current value $\alpha$
to a new value $\alpha'$. The proposal for the hyperparameter(s) is chosen
to satisfy detailed balance with respect to $p(\alpha)$.

The overall Metropolis acceptance probability
for this kind of move, if sampling the prior (or the constrained prior of DNS)
must include the following factor:
\begin{eqnarray}
\frac{\prod_{i=1}^N p(x_i | \alpha')}{\prod_{i=1}^N p(x_i | \alpha)}
\end{eqnarray}
Since this proposal leaves the objects $\{x_i\}$ fixed, it will usually not
affect the value of the likelihood, and therefore the likelihood will not need
to be recomputed.

\subsection{Proposals that change the hyperparameters and all of the objects}
The above proposals allow for changes to $N$, $\alpha$, and $\{x_i\}$,
and are therefore sufficient to allow for ``correct'' exploration of the
prior distribution, and the constrained prior distributions used in DNS.
However, they do not necessarily allow for {\it efficient} exploration, even
of the prior itself. The main reason for this is the inability for large
changes to be made to the hyperparameters $\alpha$.

>>>>

\subsection{Proposals that modify $N$}\label{sec:proposal1}
The first kind of proposal we consider are proposals that change the
dimension of the model, i.e. proposals that change the value of $N$. By
necessity, these will also change the parameters $\{x_i\}_{i=1}^N$ because
the number of parameters will be changed. The proposals used here are
traditionally called {\it birth and death} proposals.

@@

\subsection{Proposals that modify objects}\label{sec:proposal2}
We now consider a proposal distribution that modifies one or more of the
objects $\{x_i\}$, while keeping the number of objects $N$, as well as the
hyperparameters $\alpha$, fixed.

@@

\subsection{Proposals that change the hyperparameters,
keeping the objects fixed}\label{sec:proposal3}
Another kind of proposal that we will consider is a proposal that keeps all of
the objects fixed in place (i.e. leaves $\{x_i\}$) unchanged, but changes
the hyperparameter(s) from their current value $\alpha$
to a new value $\alpha'$. The proposal for the hyperparameter(s) is chosen
to satisfy detailed balance with respect to $p(\alpha)$.

The overall Metropolis acceptance probability
for this kind of move, if sampling the prior (or the constrained prior of DNS)
must include the following factor:
\begin{eqnarray}
\frac{\prod_{i=1}^N p(x_i | \alpha')}{\prod_{i=1}^N p(x_i | \alpha)}
\label{eqn:acceptance_prob}
\end{eqnarray}
Since this proposal leaves the objects $\{x_i\}$ fixed, it will usually not
affect the value of the likelihood, and therefore the likelihood will not need
to be recomputed.

\subsection{Proposals that change the hyperparameters
and all of the objects}\label{sec:proposal4}
The above proposals allow for changes to $N$, $\alpha$, and $\{x_i\}$,
and are therefore sufficient to allow for ``correct'' exploration of the
prior distribution, and the constrained prior distributions used in DNS.
However, they do not necessarily allow for {\it efficient} exploration, even
of the prior itself. The main reason for this is the inability for large
changes to be made to the hyperparameters $\alpha$. If the proposed change
from $\alpha$ to $\alpha'$ is large, the ratio in
Equation~\ref{eqn:acceptance_prob} is likely to be very small, and the move
will probably be rejected.

Therefore, we allow an additional move that changes $\alpha$ to a new
value $\alpha'$, but rather than leaving the objects $\{x_i\}$ fixed, we
drag them so they represent the distribution $p(x | \alpha')$ rather than
$p(x|\alpha)$. We do this by making use of the transformation functions
$F(x; \alpha)$ and $G(x; \alpha)$ defined in Section~\ref{sec:proposal2}.
